Spatial Relational Models for Neural Circuit Discovery

### 2013-10-21 docs/techreport.tex
additional diagnostic plots

\usepackage{csquotes}% Recommended
\usepackage{amssymb}
\usepackage{biblatex}

@@

We adopt the terminology from \autocite{Kemp}. A domain $T_n$ is a
collection of entities $\{e^t_i | i \in 0 \dots N^t -1 \} $ that share
some common property. A relation is a collection of observation
defined on a collection of domains. For example, if one domain is
``students'' and another is ``courses'', the relation
``$\operatorname{has-taken}(e^s_i, e^c_j)$ is true if student $e^s_i$ has
taken course $e^c_j$.

@@

\begin{figure}
  \centering 
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=0.3\textwidth]{logisticdistance.ai}
    \caption{Raw data}
    \label{fig:gull}
  \end{subfigure}

  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=0.3\textwidth]{exponentialdistancepoisson.ai}
    \caption{Raw data}
    \label{fig:gull}
  \end{subfigure}

@@

\subsubsection{Exponential Distance Poisson}
Some of our observations are count-valued.

@@

\subsubsection{Structural Inference}
Algorithm 8 from radford neal \cite{nealalgo8}

\subsubsection{Per-component parameters in nonconjugate case}
Slice sample on latent parameters

@@

Dense serial electron microscopy of a $VOLUMNE$ in the mouse
retina by \autocite{MouseReinta} yielded a listing of places where
neurons come into contact. There were $number$ cells originally, whcih
were refined through various classification schemes. We selected the
$NUMBER$ for which the location of the soma could be reconstruted from
the provided cell plots (soma locations were not provided by the
study's authors in machien-readble form).

@@

\subsection{Drosophila medulla}
\cite{DrosophilaConnectome}
No cell bodies -- what to use for distance? 
Human annotation
what the hell is a cell

@@

>>>>

\usepackage{csquotes}% Recommended
\usepackage{amssymb}
\usepackage[citestyle=numeric-comp,url=false,hyperref=auto,isbn=false]{biblatex}
\addbibresource{connectomics motif.bib}
\addbibresource{connectomics motif-relational models.bib}

@@

We adopt the terminology from \autocite{Kemp2006a}. A domain $T_n$ is a
collection of entities $\{e^t_i | i \in 0 \dots N^t -1 \} $ that share
some common property. A relation is a collection of observation
defined on a collection of domains. For example, if one domain is
``students'' and another is ``courses'', the relation
``$\operatorname{has-taken}(e^s_i, e^c_j)$ is true if student $e^s_i$ has
taken course $e^c_j$.

@@

\begin{figure}
  \centering 
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[height=1.5in]{logisticdistance.ai}
    \caption{Logistic-Distance Bernoulli Likelihood}
    \label{fig:gull}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[height=1.5in]{exponentialdistancepoisson.ai}
    \caption{Exponential-Distance Poisson Likelihood}
    \label{fig:gull}
  \end{subfigure}

@@

\subsubsection{Exponential Distance Poisson}
For distance-based models with count-based observations, we use an exponential

@@

\subsubsection{Structural Inference}
Algorithm 8 from radford neal \autocite{Neal2000}

\subsubsection{Per-component parameters in nonconjugate case}
Slice sample on latent parameters \autocite{Neal2003}

@@

Dense serial electron microscopy of a $VOLUMNE$ in the mouse
retina by \autocite{Helmstaedter2013} yielded a listing of places where
neurons come into contact. There were $number$ cells originally, whcih
were refined through various classification schemes. We selected the
$950$ for which the location of the soma could be reconstruted from
the provided cell plots (soma locations were not provided by the
study's authors in machien-readble form).

@@

\subsection{Drosophila medulla}
\autocite{Takemura2013}
No cell bodies -- what to use for distance? 
Human annotation
what the hell is a cell

@@

\printbibliography
